On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-01-31 docs/mvfits_paper/mvf.tex
updating cw fit comparison notebooks and plots

  \begin{tabular}{lr}
    \includegraphics[width=0.49\textwidth]{fits_w.pdf} & \includegraphics[width=0.49\textwidth]{fits_tau.pdf}

@@

    \includegraphics[width=0.49\textwidth]{res_w.pdf} & \includegraphics[width=0.49\textwidth]{res_tau.pdf}

@@

  \begin{tabular}{lr}
    \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_1.pdf} & \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_2.pdf} \\
    \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_3v2.pdf} & \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_4v2.pdf}

>>>>

  \begin{tabular}{ll}
    {\includegraphics[width=0.49\textwidth]{fits_w.pdf}} & {\includegraphics[width=0.49\textwidth]{fits_tau.pdf}}
    % \\
    % \includegraphics[width=0.49\textwidth]{res_w.pdf} & \includegraphics[width=0.49\textwidth]{res_tau.pdf}

@@

    \hspace{0.35cm}\includegraphics[width=0.43\textwidth]{res_cw_0.pdf} & \hspace{0.3cm}\includegraphics[width=0.43\textwidth]{res_cw_1.pdf}

@@

  \begin{tabular}{ll}
    \hspace{-0.21cm}\includegraphics[width=0.48\textwidth]{issue2_ysprod_1.pdf} & \includegraphics[width=0.48\textwidth]{issue2_ysprod_2.pdf} \\
    \includegraphics[width=0.48\textwidth]{issue2_ysprod_3v2.pdf} & \hspace{0.3cm}\includegraphics[width=0.48\textwidth]{issue2_ysprod_4v2.pdf}
